---
title: "BACHMI ROUTE ONLY INFECTED INDIVIDUALS(IM(n= 19)/ IV (n=6))"
output:
  html_document:
    df_print: paged
    self_contained: false

date: "2023-06-30"
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(knitr)
library(dplyr)
library(tidyr)
library(ggpubr)
library(ggbeeswarm)
library(rstatix)
library(ggplot2)
library(dunn.test)
sigcytoc1<-c()
gem.cli.df <- readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/NEW_BACHMI_database_20150721_GMP_M0.xlsx")
gem.cli.df[164,16] <- 37.7
gem.cli.df[164,17] <- 1
gem.cli.df[165,16] <- NA
gem.cli.df[165,17] <- NA
gem.cli.df[244,31] <- 0
#gem.cli.df <- gem.cli.df[,-c(21:22)]
gem.cli.df<-gem.cli.df[gem.cli.df$Malaria=="parasitemia",]
#Readall database and convert variables into factors

ck <- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/All CK_BACHMI01_22June_Susana_concentracions.csv", sep=";")
ck<-ck [ , c(1:14,45,47,49,15:44,46,48,50)]

colnames(ck)[21:50]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","CXCL13","IL-21","TGF-β")

cknorm<- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/ck_bachmi_susana_normalitzat_.csv", sep=";")

colnames(cknorm)[20:49]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","TGF-β","CXCL13","IL-21")

cknorm<-cknorm[cknorm$Malaria=="parasitemia",]

dc<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/BACHMI DC ALL 22June2015_Susana_frequencies.xlsx")
dc<-dc[dc$Malaria=="parasitemia",]

igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")
igm<-igm[igm$Malaria=="parasitemia",]

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg<-igg[igg$Malaria=="parasitemia",]


```



# Differences hemo by Route

Timepoints and data:

-D-1: 22 (17 IM, 5 IV)
-D01: 0
-D07: 0
-D21/M0: 22
-D22/M1: 0
-D23/M2: 0 
-D35: 22 
-D90: 22 

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D21"|gem.cli.df$Day=="M0", "D21/M0", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D22"|gem.cli.df$Day=="M1", "D22/M1", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D23"|gem.cli.df$Day=="M2", "D23/M2", gem.cli.df$Day)
 gem.cli.df<-gem.cli.df[!gem.cli.df$Day=="D01"& !gem.cli.df$Day=="D07"& !gem.cli.df$Day=="D22/M1",]

 hemo2<-gem.cli.df %>%
  pivot_longer(
    cols = Hemoglobin:platelet,
    names_to = 'type',
    values_to = 'counts')
dfsignificance<-c()
for (j in unique(hemo2$Day)){
  hemo3<-hemo2[hemo2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  type<-unique(hemo3$type)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      hemonew3<-hemo3[hemo3$type==i,]
      comparison<-hemonew3$Route
      pshap<-shapiro.test(hemonew3$counts)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(hemonew3$counts ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(hemonew3$counts ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, type=type, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,type)

stat.test2 <- hemo2%>%
  group_by(type, Day) %>%
  t_test(counts ~ Route) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,type)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))


for (i in colnames(gem.cli.df[20:25])){
    var_name_ticked<-paste0("`", i, "`")
    grafic<-ggplot(gem.cli.df, aes_string("Day", var_name_ticked)) +
    #facet_wrap(~ analyte) +
    xlab("Day")+ ylab("Counts")+
    geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = Route))+
    geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "bottom", legend.direction = "horizontal") +scale_colour_manual(values = c( "dodgerblue3", "gold1")) +
    ggtitle(i) 
 print(grafic+stat_pvalue_manual(stat.test2[stat.test2$type==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(hemo2$counts[hemo2$type==i])))+0.05) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 


```


# Differences DC 

Timepoints and data:

-D-1: 25 (19 IV, 6 IV)
-D01: 25
-D07: 25
-D21/M0: 25 
-D22/M1: 25
-D23/M2: 25 
-D35: 25 
-D90: 25

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
 dc$Day<-ifelse(dc$Day=="D21"|dc$Day=="M0", "D21/M0", dc$Day)
 dc$Day<-ifelse(dc$Day=="D22"|dc$Day=="M1", "D22/M1", dc$Day)
 dc$Day<-ifelse(dc$Day=="D23"|dc$Day=="M2", "D23/M2", dc$Day)

dc2<-dc %>%
  pivot_longer(
    cols = Lymphos:"immature DC",
    names_to = 'cell_population',
    values_to = 'freq')

dfsignificance<-c()
for (j in unique(dc2$Day)){
  dc3<-dc2[dc2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  cells<-unique(dc3$cell_population)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in cells){
      dcnew3<-dc3[dc3$cell_population==i,]
      comparison<-dcnew3$Route
      pshap<-shapiro.test(dcnew3$freq)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(dcnew3$freq ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(dcnew3$freq ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, cells=cells, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,cells)

stat.test2 <- dc2%>%
  group_by(cell_population, Day) %>%
  t_test(freq ~ Route) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,cell_population)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in colnames(dc[13:24])){
    var_name_ticked<-paste0("`", i, "`")
    grafic<-ggplot(dc, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+ ylab("Frequency (%)")+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = Route))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route)) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +scale_colour_manual(values = c( "dodgerblue3", "gold1"))+
        ggtitle(i) 
      print(grafic+stat_pvalue_manual(stat.test2[stat.test2$cell_population==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(dc2$freq[dc2$cell_population==i])))+3) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```


# Differences IgG & IgM Routes


All timepoints 25 participants (19 IM, 6 IV). 

P-values adjusted by FDR (all antibodies at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
igm[15:36]<-sapply(igm[15:36], log10)
igm$Day<-ifelse(igm$Day=="D21"|igm$Day=="M0", "D21/M0", igm$Day)
igm$Day<-ifelse(igm$Day=="D22"|igm$Day=="M1", "D22/M1", igm$Day)
igm$Day<-ifelse(igm$Day=="D23"|igm$Day=="M2", "D23/M2", igm$Day)
igm<-igm[!is.na(igm$Route),]

colnames(igm)[15:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4", 
"PfRH5","MSP-1 19","BSA","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2",
"DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igm2<-igm %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')

igm2$fullname<-paste(igm2$Ig, igm2$antigen, sep="_")

igg[16:36]<-sapply(igg[16:36], log10)
igg$Day<-ifelse(igg$Day=="D21"|igg$Day=="M0", "D21/M0", igg$Day)
igg$Day<-ifelse(igg$Day=="D22"|igg$Day=="M1", "D22/M1", igg$Day)
igg$Day<-ifelse(igg$Day=="D23"|igg$Day=="M2", "D23/M2", igg$Day)
igg<-igg[!is.na(igg$Route),]

colnames(igg)[16:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4",
"PfRH5","MSP-1 19","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2",
"DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igg2<-igg %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')
igg2$fullname<-paste(igg2$Ig, igg2$antigen, sep="_")
igg2<-igg2[,-15]
ig2<-rbind(igm2, igg2)
dfsignificance<-c()
for (j in unique(ig2$Day)){
  ig3<-ig2[ig2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in unique(ig3$fullname)){
      ignew3<-ig3[ig3$fullname==i,]
      comparison<-ignew3$Route
      pshap<-shapiro.test(ignew3$log10_conc)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(ignew3$log10_conc ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(ignew3$log10_conc ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=unique(ig3$fullname), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,fullname)

stat.test2 <- ig2%>%
  group_by(fullname, Day) %>%
  t_test(log10_conc ~ Route) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

colnames(igg)[16:36]<-paste("IgG",colnames(igg)[16:36], sep="_")
igg<-igg[!is.na(igg$Route),]
for (i in colnames(igg[16:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igg, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (AU)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = Route))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route))+
        theme_bw() + scale_colour_manual(values = c( "dodgerblue3", "gold1"))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 

igm<-igm[!is.na(igm$Route),]
colnames(igm)[15:36]<-paste("IgM",colnames(igm)[15:36], sep="_")
for (i in colnames(igm[15:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igm, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (AU)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = Route))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route))+
        theme_bw() + scale_colour_manual(values = c( "dodgerblue3", "gold1"))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 

```


# Citos normalized differences Routes


Timepoints and data:

-D-1: 25 (19 IM, 6 IV)
-D01: 25
-D07: 25
-D21/M0: 25 
-D22/M1: 25 
-D23/M2: 25 
-D35: 25 
-D90: 0

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 
```{r, message=FALSE, warning=FALSE, echo=FALSE}
cknorm<-cknorm[!is.na(cknorm$Route),]
cknorm<-cknorm[,-44]
cknorm<- cknorm[c(colnames(cknorm[1:16]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")]
cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
cknorm[17:48]<-sapply(cknorm[17:48], log10)

cknorm2<-cknorm %>%
  pivot_longer(
    cols = EGF:CXCL13,
    names_to = 'analyte',
    values_to = 'log10_mfi')

cknorm2$analyte<- factor(cknorm2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13"))


cknorm2<-cknorm2[!cknorm2$Day=="D90",]

cyto_names<-unique(cknorm2$analyte)
dfsignificance<-c()
for (j in unique(cknorm2$Day)){
  cknorm3<-cknorm2[cknorm2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  pvals<-c()
  for(i in cyto_names){
      cknormnew3<-cknorm3[cknorm3$analyte==i,]
      comparison<-cknormnew3$Route
      pshap<-shapiro.test(cknormnew3$log10_mfi)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(cknormnew3$log10_mfi ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(cknormnew3$log10_mfi ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,analyte)

stat.test2 <- cknorm2%>%
  group_by(analyte, Day) %>%
  t_test(log10_mfi ~ Route) %>%
  adjust_pvalue()  
stat.test2<-arrange(stat.test2,Day,analyte)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in colnames(cknorm[17:48])){
  var_name_ticked<-paste0("`", i, "`")
  cknorm<-cknorm[!cknorm$Day=="D90",]
  grafic<-ggplot(cknorm, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (mfi)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6, outlier.shape=NA, aes(color = Route))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route))+
        theme_bw() +scale_colour_manual(values = c( "dodgerblue3", "gold1"))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
 print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(cknorm2$log10_mfi[cknorm2$analyte==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 

```


# IgG1 & IgG3 differences Routes


Timepoints and data (depending on antigen, maximum 18):

-D-1: 16 (12 IM, 4 IV)
-D01: 16
-D07: 16
-M0: 16
-M1: 16
-M2: 16
-D35: 16
-D90: 16

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001.

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg1<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG1_BACHMI_v02_CarlaS_2023-11-30.csv", sep=";")
igg3<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG3_BACHMI_v02_CarlaS_2023-11-30.csv", sep=",")
igg13<-rbind(igg1, igg3)
igg13<-igg13[-15]
igg13<-merge(x = igg13, y = unique(cknorm[ , c("Volunteer", "Route")]), by = "Volunteer")
igg13.2<-igg13 %>%
  pivot_longer(
    cols = "MSP3":"EXP1",
    names_to = 'antigen',
    values_to = 'log10_mfi')
igg13.2<-igg13.2[igg13.2$log10_mfi<26486.5229,]
igg13.2$log10_mfi<- log10(igg13.2$log10_mfi)
igg13.2$fullname<-paste(igg13.2$Ig, igg13.2$antigen, sep="-")
igg13.2$Day<-ifelse(igg13.2$Day=="D1", "D01", igg13.2$Day)
igg13.2$Day<-ifelse(igg13.2$Day=="D7", "D07", igg13.2$Day)
igg13.2<-igg13.2[!is.na(igg13.2$log10_mfi),]
igg13.2<-igg13.2[!igg13.2$log10_mfi=="-Inf",]

igg13.2$Day<-factor(igg13.2$Day, levels=c("D-1", "D01", "D07", "M0", "M1", "M2", "D35", "D90"))
# igg13.2<-igg13.2[!igg13.2$antigen=="PfRH5",]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-LSA1"& igg13.2$Day=="D01"),] 

igg13.2<-igg13.2[!(igg13.2$Ig=="IgG3"),]
 igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D-1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D35"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D90"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="D90"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_3D7" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_3D7" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_FVO" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfAARP" & igg13.2$Day=="M2"),]


igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="D01"),]

```

## 1. Boxplots of the significant different IgG1 & IgG3 (pval<0.05)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dfsignificance<-c()
for (j in unique(igg13.2$Day)){
  igg13.3<-igg13.2[igg13.2$Day==j,]
  pvals<-c()
  for(i in unique(igg13.3$fullname)){
      ignew3<-igg13.3[igg13.3$fullname==i,]
      comparison<-ignew3$Route
      pshap<-shapiro.test(ignew3$log10_mfi)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(ignew3$log10_mfi ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(ignew3$log10_mfi ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(ignew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(ignew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=unique(igg13.3$fullname), padj=pvals))
}
dfsignificance<-arrange(dfsignificance,Day,fullname)

stat.test2 <- igg13.2%>%
  group_by(fullname, Day) %>%
  wilcox_test(log10_mfi ~ Route) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in unique(dfsignificance$fullname)){
    subset_data<-subset(igg13.2, fullname==i)
    grafic<-ggplot(subset_data, aes(x=Day, y=log10_mfi)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (mfi)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = Route))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = Route)) +
        theme_bw() +scale_colour_manual(values = c( "dodgerblue3", "gold1"))+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
    print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(igg13.2$log10_mfi[igg13.2$fullname==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```
