---
title: "BACHMI GROUPS 36 individuals"
output:
  html_document:
    df_print: paged
    self_contained: false

date: "2023-06-30"
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(knitr)
library(dplyr)
library(tidyr)
library(ggpubr)
library(ggbeeswarm)
library(rstatix)
library(ggplot2)
library(dunn.test)
sigcytoc1<-c()
gem.cli.df <- readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/NEW_BACHMI_database_20150721_GMP_M0.xlsx")
gem.cli.df[164,16] <- 37.7
gem.cli.df[164,17] <- 1
gem.cli.df[165,16] <- NA
gem.cli.df[165,17] <- NA
gem.cli.df[244,31] <- 0
#gem.cli.df <- gem.cli.df[,-c(21:22)]

#Readall database and convert variables into factors

cknorm<- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/ck_bachmi_susana_normalitzat_.csv", sep=";")

colnames(cknorm)[20:49]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","TGF-β","CXCL13","IL-21")


dc<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/BACHMI DC ALL 22June2015_Susana_frequencies.xlsx")

igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")

group.colors <- c("1" = "#F8766D", "2" = "#B79F00", "3" ="#00BA38", "4" = "#00BFC4", "5" = "#619CFF", "6"="#F564E3")

```



# Differences hemo by Group 

Timepoints and data:

-D-1: 24 (Group1: 6, Group3: 1, Group4: 5, Group5: 6, Group6: 6)
-D01: 0
-D07: 0
-D21/M0: 24 
-D22/M1: 2 (Group6: 2)
-D23/M2: 18 (Group1: 2, Group4: 5, Group5: 5, Group6: 6)
-D35: 24 
-D90: 24 

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D21"|gem.cli.df$Day=="M0", "D21/M0", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D22"|gem.cli.df$Day=="M1", "D22/M1", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D23"|gem.cli.df$Day=="M2", "D23/M2", gem.cli.df$Day)
 hemo<- gem.cli.df[,c(20:25)]

 hemo2<-gem.cli.df %>%
  pivot_longer(
    cols = Hemoglobin:platelet,
    names_to = 'type',
    values_to = 'counts')
hemo2<-hemo2[!hemo2$Day=="D01"& !hemo2$Day=="D07" & !hemo2$Day=="D22/M1",]
hemo2$Group<-factor(hemo2$Group)
hemo2<-hemo2[!is.na(hemo2$counts),]

dfsignificance<-c()

for (j in unique(hemo2$Day)){
  hemo3<-hemo2[hemo2$Day==j,]
  pvalue<-c()
  type<-unique(hemo3$type)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      hemonew3<-hemo3[hemo3$type==i,]
        comparison<-hemonew3$Group
      pshap<-shapiro.test(hemonew3$counts)$p.value
      if (pshap >0.05){
        result_anova <- aov(counts ~ Group, data = hemonew3)
        p_value_anova <- summary(result_anova)[[1]]$`Pr(>F)`[1]
           tukey_result <- TukeyHSD(result_anova)
            sigcytoc1<-c(sigcytoc1,i,j, tukey_result$Group[,4][tukey_result$Group[,4]<0.05])
            rownames(tukey_result$Group)<-paste(sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[2]), sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[1]), sep="-")
            group<-rownames(tukey_result$Group)
            padj<-tukey_result$Group[,4]
      }
      else{
        result_kw <- kruskal.test(counts ~ Group, data = hemonew3)
         capture.output(result_dunn <-
                   as.data.frame(dunn.test(hemonew3$counts, hemonew3$Group,
                       table = FALSE,
                       kw = FALSE,
                       label = FALSE,
                       alpha = 0.05
                   )), file = "NULL")
        sigcytoc1<-c(sigcytoc1,i,j,result_dunn$comparisons[result_dunn$P.adjusted<0.05],result_dunn$P.adjusted[result_dunn$P.adjusted<0.05])
        group<-result_dunn$comparisons
        padj<-result_dunn$P.adjusted
      }
        dfsignificance<-rbind(dfsignificance,data.frame(Day=j, type=i, group=group, padj=padj)) 
}
}

dfsignificance<-arrange(dfsignificance,Day,type, group)

hemo4<-hemo2
p<-hemo4[rep(grep("3", hemo4$Group), 2),]
p$counts<-runif(48)
hemo4<-rbind(hemo4,p)

stat.test <- hemo4 %>%
   group_by(Day, type) %>%
   t_test(counts ~ Group)
 
 stat.test2<-arrange(stat.test,Day,type, group1)
 stat.test2$p.adj<-dfsignificance$padj
 stat.test2<-stat.test2%>%
  add_significance("p.adj") 
 stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))
  gem.cli.df<-gem.cli.df[!gem.cli.df$Group=="2",]

gem.cli.df$Group<-factor(gem.cli.df$Group)

gem.cli.df<-gem.cli.df[!gem.cli.df$Day=="D01"& !gem.cli.df$Day=="D07" &!gem.cli.df$Day=="D22/M1",]
for (i in colnames(gem.cli.df[20:25])[-2]){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(gem.cli.df, aes_string("Day", var_name_ticked)) + ylab(paste(i, "Counts"))+
          geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()+scale_fill_manual(values=group.colors)+ scale_color_manual(values=group.colors)
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$type==i,], label = "p.adj.signif", hide.ns = TRUE,bracket.nudge.y = -0.00001, tip.length = 0.01))
 } 
for (i in colnames(gem.cli.df[21])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(gem.cli.df, aes_string("Day", var_name_ticked)) + ylab(paste(i, "Counts"))+
          geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()+scale_fill_manual(values=group.colors)+ scale_color_manual(values=group.colors)
  print(grafic)
 } 
```


	

# Differences DC 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
 dc$Day<-ifelse(dc$Day=="D21"|dc$Day=="M0", "D21/M0", dc$Day)
 dc$Day<-ifelse(dc$Day=="D22"|dc$Day=="M1", "D22/M1", dc$Day)
 dc$Day<-ifelse(dc$Day=="D23"|dc$Day=="M2", "D23/M2", dc$Day)
```
Timepoints and data:

-D-1: 36 (Group1: 4, Group2: 1, Group3: 2, Group4: 6, Group5: 6, Group6: 6)
-D01: 36
-D07: 36
-D21/M0: 36 
-D22/M1: 24 (Group1: 4, Group2: 1, Group3: 2, Group4: 5, Group5: 6, Group6: 6)
-D23/M2: 36 
-D35: 36 
-D90: 36

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(dunn.test)
dc2<-dc %>%
  pivot_longer(
    cols = Lymphos:"immature DC",
    names_to = 'cell_population',
    values_to = 'freq')
hemo2$Group<-factor(hemo2$Group)
sigcytoc1<-c()
dc2$Group<-factor(dc2$Group)

sigcytoc1<-c()
dc2$Group<-factor(dc2$Group)
dfsignificance<-c()
for (j in unique(dc2$Day)){
  dc3<-dc2[dc2$Day==j,]
  pvalue<-c()
  type<-unique(dc3$cell_population)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      dcnew3<-dc3[dc3$cell_population==i,]
        comparison<-dcnew3$Group
      pshap<-shapiro.test(dcnew3$freq)$p.value
      if (pshap >0.05){
        result_anova <- aov(freq ~ Group, data = dcnew3)
        p_value_anova <- summary(result_anova)[[1]]$`Pr(>F)`[1]
           tukey_result <- TukeyHSD(result_anova)
            sigcytoc1<-c(sigcytoc1,i,j, tukey_result$Group[,4][tukey_result$Group[,4]<0.05])
            
            rownames(tukey_result$Group)<-paste(sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[2]), sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[1]), sep="-")
            group<-rownames(tukey_result$Group)
            padj<-tukey_result$Group[,4]
      }
      else{
        result_kw <- kruskal.test(freq ~ Group, data = dcnew3)
         capture.output(result_dunn <-
                   as.data.frame(dunn.test(dcnew3$freq, dcnew3$Group,
                       table = FALSE,
                       kw = FALSE,
                       label = FALSE,
                       alpha = 0.05
                   )), file = "NULL")
        sigcytoc1<-c(sigcytoc1,i,j,result_dunn$comparisons[result_dunn$P.adjusted<0.05],result_dunn$P.adjusted[result_dunn$P.adjusted<0.05])
        group<-result_dunn$comparisons
        padj<-result_dunn$P.adjusted
      }
        dfsignificance<-rbind(dfsignificance,data.frame(Day=j, cell_population=i, group=group, padj=padj)) 
}
}

dfsignificance<-arrange(dfsignificance,Day,cell_population, group)


stat.test <- dc2 %>%
  group_by(Day, cell_population) %>%
  t_test(freq ~ Group)

stat.test2<-arrange(stat.test,Day,cell_population, group1)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 
stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

dc$Group<-factor(dc$Group)
for (i in colnames(dc[13:24])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(dc, aes_string("Day", var_name_ticked)) + ylab(paste("Frequency ",i, "(%)"))+
    geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$cell_population==i,], label = "p.adj.signif", hide.ns = TRUE,bracket.nudge.y = -0.00001, tip.length = 0.01))
 } 
```


# Differences IgG & IgM 

All timepoints 36 participants. 

P-values adjusted by FDR (all antibodies at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}

igm[15:36]<-sapply(igm[15:36], log10)
igm$Day<-ifelse(igm$Day=="D21"|igm$Day=="M0", "D21/M0", igm$Day)
igm$Day<-ifelse(igm$Day=="D22"|igm$Day=="M1", "D22/M1", igm$Day)
igm$Day<-ifelse(igm$Day=="D23"|igm$Day=="M2", "D23/M2", igm$Day)
colnames(igm)[15:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4", "PfRH5","MSP-1 19","BSA","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2", "DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igm2<-igm %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')

igm2$fullname<-paste(igm2$Ig, igm2$antigen, sep="_")

igg[16:36]<-sapply(igg[16:36], log10)
igg$Day<-ifelse(igg$Day=="D21"|igg$Day=="M0", "D21/M0", igg$Day)
igg$Day<-ifelse(igg$Day=="D22"|igg$Day=="M1", "D22/M1", igg$Day)
igg$Day<-ifelse(igg$Day=="D23"|igg$Day=="M2", "D23/M2", igg$Day)
colnames(igg)[16:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4", "PfRH5","MSP-1 19","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2", "DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igg2<-igg %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')
igg2$fullname<-paste(igg2$Ig, igg2$antigen, sep="_")
igg2<-igg2[,-15]
ig2<-rbind(igm2, igg2)
sigcytoc1<-c()
ig2$Group<-factor(ig2$Group)

sigcytoc1<-c()
ig2$Group<-factor(ig2$Group)
dfsignificance<-c()
for (j in unique(ig2$Day)){
  ig3<-ig2[ig2$Day==j,]
  pvalue<-c()
  type<-unique(ig3$fullname)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      ignew3<-ig3[ig3$fullname==i,]
        comparison<-ignew3$Group
      pshap<-shapiro.test(ignew3$log10_conc)$p.value
      if (pshap >0.05){
        result_anova <- aov(log10_conc ~ Group, data = ignew3)
        p_value_anova <- summary(result_anova)[[1]]$`Pr(>F)`[1]
           tukey_result <- TukeyHSD(result_anova)
            sigcytoc1<-c(sigcytoc1,i,j, tukey_result$Group[,4][tukey_result$Group[,4]<0.05])
            
            rownames(tukey_result$Group)<-paste(sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[2]), sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[1]), sep="-")
            group<-rownames(tukey_result$Group)
            padj<-tukey_result$Group[,4]
      }
      else{
        result_kw <- kruskal.test(log10_conc ~ Group, data = ignew3)
        #result_dunn<-dunn.test(ignew3$log10_conc, ignew3$Group, table=FALSE, kw=FALSE, label=FALSE)
         capture.output(result_dunn <-
                   as.data.frame(dunn.test(ignew3$log10_conc, ignew3$Group,
                       table = FALSE,
                       kw = FALSE,
                       label = FALSE,
                       alpha = 0.05
                   )), file = "NULL")
        sigcytoc1<-c(sigcytoc1,i,j,result_dunn$comparisons[result_dunn$P.adjusted<0.05],result_dunn$P.adjusted[result_dunn$P.adjusted<0.05])
        group<-result_dunn$comparisons
        padj<-result_dunn$P.adjusted
      }
        dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=i, group=group, padj=padj)) 
}
}

dfsignificance<-arrange(dfsignificance,Day,fullname, group)

stat.test <- ig2 %>%
  group_by(Day, fullname) %>%
  t_test(log10_conc ~ Group)


stat.test2<-arrange(stat.test,Day,fullname, group1)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))




colnames(igg)[16:36]<-paste("IgG",colnames(igg)[16:36], sep="_")
igg$Group<-factor(igg$Group)

for (i in colnames(igg[16:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igg, aes_string("Day",var_name_ticked)) + ylab(paste("log10(",i, ")"))+
          geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  tip.length = 0.01,  bracket.nudge.y = -0.00001))
} 

colnames(igm)[15:36]<-paste("IgM",colnames(igm)[15:36], sep="_")
igm$Group<-factor(igm$Group)
for (i in colnames(igm[15:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igm, aes_string("Day", var_name_ticked)) + ylab(paste("log10(",i, ")"))+
          geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  tip.length = 0.01,  bracket.nudge.y = -0.00001))
} 
```




<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- ck$Day[37]<-"D22" -->
<!-- ck$Day<-ifelse(ck$Day=="D21"|ck$Day=="M0", "D21/M0", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D22"|ck$Day=="M1", "D22/M1", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D23"|ck$Day=="M2", "D23/M2", ck$Day) -->
<!-- ``` -->



<!-- # Citos not normalized differences -->

<!-- Timepoints and data: -->

<!-- -D-1: 36 (16 male, 20 female) -->
<!-- -D01: 36 -->
<!-- -D07: 36 -->
<!-- -D21/M0: 36  -->
<!-- -D22/M1: 36  -->
<!-- -D23/M2: 36  -->
<!-- -D35: 36  -->
<!-- -D90: 0 -->

<!-- #P-values adjusted by FDR (all analytes at each timepoint).  -->
<!--  \*:p.adj < 0.05 -->
<!--  \*\*: p.adj < 0.01 -->
<!--  \*\*\*: p.adj < 0.001,  -->
<!--  \*\*\*\*: p.adj < 0.0001.  -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- ck<- ck[c(colnames(ck[1:17]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")] -->
<!-- ck[18:50]<-sapply(ck[18:50], log10) -->
<!-- ck2<-ck %>% -->
<!--   pivot_longer( -->
<!--     cols = EGF:CXCL13, -->
<!--     names_to = 'analyte', -->
<!--     values_to = 'log10_mfi') -->
<!-- ck2$analyte<- factor(ck2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")) -->

<!-- ck2<-ck2[!ck2$Day=="D90",] -->
<!-- ck2<-ck2[!ck2$analyte=="IL-17",] -->

<!-- cyto_names<-unique(ck2$analyte) -->
<!-- dfsignificance<-c() -->
<!-- for (j in unique(ck2$Day)){ -->
<!--   ck3<-ck2[ck2$Day==j,] -->
<!--   sigcytoc1<-c() -->
<!--   pvalue<-c() -->
<!--   pvals<-c() -->
<!--   for(i in cyto_names){ -->
<!--       cknew3<-ck3[ck3$analyte==i,] -->
<!--       comparison<-cknew3$sex -->
<!--       pshap<-shapiro.test(cknew3$log10_mfi)$p.value -->
<!--       if (pshap <0.05){ -->
<!--           wilc<-wilcox.test(cknew3$log10_mfi ~ comparison)$p.value -->
<!--           pvals<-c(pvals, wilc) -->
<!--           #wilc<-p.adjust(wilc) -->
<!--           if (wilc< 0.05){ -->
<!--               sigcytoc1<-c(i,wilc,sigcytoc1) -->
<!--           } -->
<!--       } -->
<!--       else{ -->
<!--           variance<-var.test(cknew3$log10_mfi ~ comparison)$p.value  -->
<!--           if (variance< 0.05){ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value -->
<!--               #ttest<-p.adjust(ttest) -->
<!--               pvals<-c(pvals, ttest) -->

<!--           } -->
<!--           else{ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value -->
<!--               #ttest<-p.adjust(ttest) -->
<!--               pvals<-c(pvals, ttest)      -->
<!--           } -->
<!--           if (ttest< 0.05){ -->
<!--               sigcytoc1<-c(i,ttest,sigcytoc1) -->
<!--               pvalue<-c(ttest,pvalue)} -->
<!--       }} -->
<!--   padj<-p.adjust(pvals,method = "fdr") -->
<!-- dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj)) -->
<!-- } -->
<!-- dfsignificance<-arrange(dfsignificance,Day,analyte) -->

<!-- stat.test2 <- ck2%>% -->
<!--   group_by(analyte, Day) %>% -->
<!--   t_test(log10_mfi ~ sex) %>% -->
<!--   adjust_pvalue()   -->
<!-- stat.test2<-arrange(stat.test2,Day,analyte) -->
<!-- stat.test2$p.adj<-dfsignificance$padj -->
<!-- stat.test2<-stat.test2%>% -->
<!--   add_significance("p.adj")  -->

<!-- stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y")) -->


<!-- for (i in colnames(ck[18:50])[-24]){ -->
<!--   var_name_ticked<-paste0("`", i, "`") -->
<!--   grafic<-ggplot(ck, aes_string("Day", var_name_ticked)) + -->
<!--           geom_boxplot(position=position_dodge(1), aes(fill=sex)) -->
<!--   print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ck2$log10_mfi[ck2$analyte==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))) -->
<!-- }  -->
<!-- ``` -->



# Citos normalized differences 


Timepoints and data:

All timepoints 36 participants. 


#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 
```{r, message=FALSE, warning=FALSE, echo=FALSE}

cknorm<- cknorm[c(colnames(cknorm[1:16]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")]
cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
cknorm[17:49]<-sapply(cknorm[17:49], log10)
cknorm2<-cknorm %>%
  pivot_longer(
    cols = EGF:CXCL13,
    names_to = 'analyte',
    values_to = 'log10_mfi')
cknorm2$analyte<- factor(cknorm2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13"))

cknorm2<-cknorm2[!cknorm2$Day=="D90",]
cknorm2<-cknorm2[!cknorm2$analyte=="IL-17",]

cyto_names<-unique(cknorm2$analyte)

sigcytoc1<-c()
cknorm2$Group<-factor(cknorm2$Group)
dfsignificance<-c()
for (j in unique(cknorm2$Day)){
  cknorm3<-cknorm2[cknorm2$Day==j,]
  pvalue<-c()
  type<-unique(cknorm3$analyte)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      cknormnew3<-cknorm3[cknorm3$analyte==i,]
        comparison<-cknormnew3$Group
      pshap<-shapiro.test(cknormnew3$log10_mfi)$p.value
      if (pshap >0.05){
        result_anova <- aov(log10_mfi ~ Group, data = cknormnew3)
        p_value_anova <- summary(result_anova)[[1]]$`Pr(>F)`[1]
           tukey_result <- TukeyHSD(result_anova)
            sigcytoc1<-c(sigcytoc1,i,j, tukey_result$Group[,4][tukey_result$Group[,4]<0.05])
            rownames(tukey_result$Group)<-paste(sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[2]), sapply(strsplit(rownames(tukey_result$Group), "-"), function(x) x[1]), sep="-")
            group<-rownames(tukey_result$Group)
            padj<-tukey_result$Group[,4]
      }
      else{
        result_kw <- kruskal.test(log10_mfi ~ Group, data = cknormnew3)
       # result_dunn<-dunn.test(cknormnew3$log10_mfi, cknormnew3$Group, table=FALSE, kw=FALSE, label=FALSE)
        capture.output(result_dunn <-
                   as.data.frame(dunn.test(cknormnew3$log10_mfi, cknormnew3$Group,
                       table = FALSE,
                       kw = FALSE,
                       label = FALSE,
                       alpha = 0.05
                   )), file = "NULL")

        sigcytoc1<-c(sigcytoc1,i,j,result_dunn$comparisons[result_dunn$P.adjusted<0.05],result_dunn$P.adjusted[result_dunn$P.adjusted<0.05])
        group<-result_dunn$comparisons
        padj<-result_dunn$P.adjusted
      }
        dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=i, group=group, padj=padj)) 
}
}

dfsignificance$analyte<- factor(dfsignificance$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13"))
dfsignificance2<-arrange(dfsignificance,Day,analyte, group)


stat.test <- cknorm2 %>%
  group_by(Day, analyte) %>%
  t_test(log10_mfi ~ Group)

stat.test2<-arrange(stat.test,Day,analyte, group1)

stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

cknorm$Group<-factor(cknorm$Group)
cknorm<-cknorm[!cknorm$Day=="D90",]

for (i in colnames(cknorm[17:49])[-24]){
var_name_ticknormed<-paste0("`", i, "`")
grafic<-ggplot(cknorm, aes_string("Day", var_name_ticknormed)) + ylab(paste("log10(",i, ")"))+
    geom_boxplot(position=position_dodge(1), aes(fill=Group), outlier.shape = NA, alpha=0.6) +   geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = Group))+ theme_bw()
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  tip.length = 0.01,    bracket.nudge.y = -0.00001))
        
} 

```



# IgG1 & IgG3 differences Groups


Timepoints and data (depending on antigen, maximum 18):all infected

-D-1: 18 (Group1: 4, Group3: 2, Group4: 4, Group5: 4, Group6: 4)
-D01: 18
-D07: 18
-M0: 18
-M1: 18
-M2: 18
-D35: 18
-D90: 18

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001.

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg1<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG1_BACHMI_v02_CarlaS_2023-11-30.csv", sep=";")
igg3<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG3_BACHMI_v02_CarlaS_2023-11-30.csv", sep=",")
igg13<-rbind(igg1, igg3)
igg13<-igg13[-15]
igg13<-merge(x = igg13, y = unique(cknorm[ , c("Volunteer", "Group")]), by = "Volunteer")
igg13.2<-igg13 %>%
  pivot_longer(
    cols = "MSP3":"EXP1",
    names_to = 'antigen',
    values_to = 'log10_mfi')
igg13.2<-igg13.2[igg13.2$log10_mfi<26486.5229,]
igg13.2$log10_mfi<- log10(igg13.2$log10_mfi)
igg13.2$fullname<-paste(igg13.2$Ig, igg13.2$antigen, sep="-")
igg13.2$Day<-ifelse(igg13.2$Day=="D1", "D01", igg13.2$Day)
igg13.2$Day<-ifelse(igg13.2$Day=="D7", "D07", igg13.2$Day)
igg13.2<-igg13.2[!is.na(igg13.2$log10_mfi),]
igg13.2<-igg13.2[!igg13.2$log10_mfi=="-Inf",]

igg13.2$Day<-factor(igg13.2$Day, levels=c("D-1", "D01", "D07", "M0", "M1", "M2", "D35", "D90"))
# igg13.2<-igg13.2[!igg13.2$antigen=="PfRH5",]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-LSA1"& igg13.2$Day=="D01"),]  #Tots els low tenen NAja que els valos abans de log10 eren negatius
# 
# igg13.2<-igg13.2[!(igg13.2$Ig=="IgG3"),]
# 
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D-1"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M0"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D07"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M2"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D35"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="D90"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="D90"),]
# 
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5" & igg13.2$Day=="M1"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M2"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="D07"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M0"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M0"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_3D7" & igg13.2$Day=="M0"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_19" & igg13.2$Day=="M0"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M1"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-LSA1" & igg13.2$Day=="M2"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_3D7" & igg13.2$Day=="M2"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_FVO" & igg13.2$Day=="M2"),]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfAARP" & igg13.2$Day=="M2"),]
# 
# 
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="D01"),]

```

## 1. Boxplots of the significant different IgG1 & IgG3 (pval<0.05)

```{r, message=FALSE, warning=FALSE, echo=FALSE}

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PfRH5"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PfRH4"),]


igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="D35"),]
sigcytoc1<-c()
igg13.2$group<-factor(igg13.2$group)
dfsignificance<-c()
for (j in unique(igg13.2$Day)){
  igg13.3<-igg13.2[igg13.2$Day==j,]
  pvalue<-c()
  type<-unique(igg13.3$fullname)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      ignew3<-igg13.3[igg13.3$fullname==i,]
        comparison<-ignew3$group
      pshap<-shapiro.test(ignew3$log10_mfi)$p.value
      if (pshap >0.05){
        result_anova <- aov(log10_mfi ~ group, data = ignew3)
        p_value_anova <- summary(result_anova)[[1]]$`Pr(>F)`[1]
           tukey_result <- TukeyHSD(result_anova)
            sigcytoc1<-c(sigcytoc1,i,j, tukey_result$group[,4][tukey_result$group[,4]<0.05])
            rownames(tukey_result$group)<-paste(sapply(strsplit(rownames(tukey_result$group), "-"), function(x) x[2]), sapply(strsplit(rownames(tukey_result$group), "-"), function(x) x[1]), sep="-")
            group<-rownames(tukey_result$group)
            padj<-tukey_result$group[,4]
      }
      else{
        result_kw <- kruskal.test(log10_mfi ~ group, data = ignew3)
        #result_dunn<-dunn.test(ignew3$log10_mfi, ignew3$group, table=FALSE, kw=FALSE, label=FALSE)
         capture.output(result_dunn <-
                   as.data.frame(dunn.test(ignew3$log10_mfi, ignew3$group,
                       table = FALSE,
                       kw = FALSE,
                       label = FALSE,
                       alpha = 0.05
                   )), file = "NULL")
        sigcytoc1<-c(sigcytoc1,i,j,result_dunn$comparisons[result_dunn$P.adjusted<0.05],result_dunn$P.adjusted[result_dunn$P.adjusted<0.05])
        group<-result_dunn$comparisons
        padj<-result_dunn$P.adjusted
      }
        dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=i, group=group, padj=padj)) 
}
}

dfsignificance<-arrange(dfsignificance,Day,fullname, group)

igg13.4<-igg13.2

p<-igg13.4[rep(grep("1", igg13.4$group), 2),]
p$log10_mfi<-runif(1834)
igg13.4<-rbind(igg13.4,p)


p<-igg13.4[rep(grep("3", igg13.4$group), 2),]
p$log10_mfi<-runif(996)
igg13.4<-rbind(igg13.4,p)
igg13.4$group<-as.factor(igg13.4$group)

stat.test2 <- igg13.4%>%
  group_by(fullname, Day) %>%
  rstatix::wilcox_test(log10_mfi ~ group) %>%
  adjust_pvalue() 

stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in unique(dfsignificance$fullname)){
    subset_data<-subset(igg13.2, fullname==i)
    grafic<-ggplot(subset_data, aes(x=Day, y=log10_mfi)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (mfi)))+
        geom_boxplot(position=position_dodge(1), aes(fill=group), outlier.shape = NA, alpha=0.6)+    geom_point(position=position_jitterdodge(jitter.width = 0.5), aes(color = group))+ theme_bw()+ scale_fill_manual(values=group.colors)+ scale_color_manual(values=group.colors)+
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  tip.length = 0.01))
} 

```


