---
title: "bachmi_responders"
output: html_document
date: "2023-11-15"
---


```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(knitr)
library(dplyr)
library(tidyr)
library(ggpubr)
library(ggbeeswarm)
library(rstatix)
library(ggplot2)
library(gridExtra)
library(lme4)
gem.cli.df <- readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/NEW_BACHMI_database_20150721_GMP_M0.xlsx")
gem.cli.df[164,16] <- 37.7
gem.cli.df[164,17] <- 1
gem.cli.df[165,16] <- NA
gem.cli.df[165,17] <- NA
gem.cli.df[244,31] <- 0
gem.cli.df$Malaria<-factor(gem.cli.df$Malaria, levels = c("parasitemia", "no parasitemia"))
gem.cli.df$responder<-factor(gem.cli.df$responder, levels = c("low", "high"))
#gem.cli.df <- gem.cli.df[,-c(21:22)]

#Readall database and convert variables into factors

ck <- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/All CK_BACHMI01_22June_Susana_concentracions.csv", sep=";")
ck<-ck [ , c(1:14,45,47,49,15:44,46,48,50)]
ck$Malaria<-factor(ck$Malaria, levels = c("parasitemia", "no parasitemia"))
ck$Day[37]<-"D22"
colnames(ck)[21:50]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","CXCL13","IL-21","TGF-β")
ck$responder<-factor(ck$responder, levels = c("low", "high"))

cknorm<- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/ck_bachmi_susana_normalitzat_.csv", sep=";")
colnames(cknorm)[20:49]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","TGF-β","CXCL13","IL-21")
cknorm$Malaria<-factor(cknorm$Malaria, levels = c("parasitemia", "no parasitemia"))
cknorm$responder<-factor(cknorm$responder, levels = c("low", "high"))

dc<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/BACHMI DC ALL 22June2015_Susana_frequencies.xlsx")
dc$Malaria<-factor(dc$Malaria, levels = c("parasitemia", "no parasitemia"))
dc$responder<-factor(dc$responder, levels = c("low", "high"))


igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")
igm$Malaria<-factor(igm$Malaria, levels = c("parasitemia", "no parasitemia"))
igm$responder<-factor(igm$responder, levels = c("low", "high"))

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg$Malaria<-factor(igg$Malaria, levels = c("parasitemia", "no parasitemia"))
igg$responder<-factor(igg$responder, levels = c("low", "high"))

```



# Differences hemo high vs low responders

Timepoints and data:

-D-1: 22 (14 high, 8 low)
-D01: 0
-D07: 0
-D21/M0: 22 (14 high, 8 low)
-D22/M1: 2(2 high, 0 low)
-D23/M2: 19 (11 high, 7 low)
-D35: 24 22 (14 high, 8 low)
-D90: 24 22 (14 high, 8 low)

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}

 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D21"|gem.cli.df$Day=="M0", "D21/M0", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D22"|gem.cli.df$Day=="M1", "D22/M1", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D23"|gem.cli.df$Day=="M2", "D23/M2", gem.cli.df$Day)
 gem.cli.df<-gem.cli.df[!gem.cli.df$Day=="D01"& !gem.cli.df$Day=="D07"& !gem.cli.df$Day=="D22/M1"&!gem.cli.df$Day=="D23/M2",]
gem.cli.df<-gem.cli.df[!is.na(gem.cli.df$responder),]

 hemo2<-gem.cli.df %>%
  pivot_longer(
    cols = Hemoglobin:platelet,
    names_to = 'type',
    values_to = 'counts')
dfsignificance<-c()
for (j in unique(hemo2$Day)){
  hemo3<-hemo2[hemo2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  type<-unique(hemo3$type)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      hemonew3<-hemo3[hemo3$type==i,]
      comparison<-hemonew3$responder
      pshap<-shapiro.test(hemonew3$counts)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(hemonew3$counts ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(hemonew3$counts ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, type=type, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,type)

stat.test2 <- hemo2%>%
  group_by(type, Day) %>%
  t_test(counts ~ responder) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,type)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))


for (i in colnames(gem.cli.df[20:25])){
    var_name_ticked<-paste0("`", i, "`")
    grafic<-ggplot(gem.cli.df, aes_string("Day", var_name_ticked)) +
    #facet_wrap(~ analyte) +
    xlab("Day")+ ylab("Counts")+
    geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+
    geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder)) +
    scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          legend.position = "bottom", legend.direction = "horizontal") +
    ggtitle(i) 
 print(grafic+stat_pvalue_manual(stat.test2[stat.test2$type==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(hemo2$counts[hemo2$type==i])))+0.05) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 
```


# Differences DC high vs low responders

Timepoints and data:

-D-1: 22 (14 high, 8 low)
-D01: 22
-D07: 22
-D21/M0: 22 
-D22/M1: 22 (13 high, 8 low)
-D23/M2: 22 
-D35: 22 
-D90: 22


#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}

 dc$Day<-ifelse(dc$Day=="D21"|dc$Day=="M0", "D21/M0", dc$Day)
 dc$Day<-ifelse(dc$Day=="D22"|dc$Day=="M1", "D22/M1", dc$Day)
 dc$Day<-ifelse(dc$Day=="D23"|dc$Day=="M2", "D23/M2", dc$Day)
 dc<-dc[!is.na(dc$responder),]

dc2<-dc %>%
  pivot_longer(
    cols = Lymphos:"immature DC",
    names_to = 'cell_population',
    values_to = 'freq')

dfsignificance<-c()
for (j in unique(dc2$Day)){
  dc3<-dc2[dc2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  cells<-unique(dc3$cell_population)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in cells){
      dcnew3<-dc3[dc3$cell_population==i,]
      comparison<-dcnew3$responder
      pshap<-shapiro.test(dcnew3$freq)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(dcnew3$freq ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(dcnew3$freq ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, cells=cells, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,cells)

stat.test2 <- dc2%>%
  group_by(cell_population, Day) %>%
  t_test(freq ~ responder) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,cell_population)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in colnames(dc[13:24])){
    var_name_ticked<-paste0("`", i, "`")
    grafic<-ggplot(dc, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+ ylab("Frequency (%)")+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder)) +
        scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
      print(grafic+stat_pvalue_manual(stat.test2[stat.test2$cell_population==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(dc2$freq[dc2$cell_population==i])))+3) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```


# Differences IgG & IgM high vs low responders


All timepoints 22 participants. 

P-values adjusted by FDR (all antibodies at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
igm[15:36]<-sapply(igm[15:36], log10)
igm$Day<-ifelse(igm$Day=="D21"|igm$Day=="M0", "D21/M0", igm$Day)
igm$Day<-ifelse(igm$Day=="D22"|igm$Day=="M1", "D22/M1", igm$Day)
igm$Day<-ifelse(igm$Day=="D23"|igm$Day=="M2", "D23/M2", igm$Day)
igm<-igm[!is.na(igm$responder),]

colnames(igm)[15:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4", 
"PfRH5","MSP-1 19","BSA","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2",
"DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igm2<-igm %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')

igm2$fullname<-paste(igm2$Ig, igm2$antigen, sep="_")

igg[16:36]<-sapply(igg[16:36], log10)
igg$Day<-ifelse(igg$Day=="D21"|igg$Day=="M0", "D21/M0", igg$Day)
igg$Day<-ifelse(igg$Day=="D22"|igg$Day=="M1", "D22/M1", igg$Day)
igg$Day<-ifelse(igg$Day=="D23"|igg$Day=="M2", "D23/M2", igg$Day)
igg<-igg[!is.na(igg$responder),]

colnames(igg)[16:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4",
"PfRH5","MSP-1 19","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2",
"DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igg2<-igg %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')
igg2$fullname<-paste(igg2$Ig, igg2$antigen, sep="_")
igg2<-igg2[,-15]
ig2<-rbind(igm2, igg2)
dfsignificance<-c()
for (j in unique(ig2$Day)){
  ig3<-ig2[ig2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in unique(ig3$fullname)){
      ignew3<-ig3[ig3$fullname==i,]
      comparison<-ignew3$responder
      pshap<-shapiro.test(ignew3$log10_conc)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(ignew3$log10_conc ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(ignew3$log10_conc ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=unique(ig3$fullname), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,fullname)

stat.test2 <- ig2%>%
  group_by(fullname, Day) %>%
  t_test(log10_conc ~ responder) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

colnames(igg)[16:36]<-paste("IgG",colnames(igg)[16:36], sep="_")
igg<-igg[!is.na(igg$responder),]
for (i in colnames(igg[16:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igg, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (AU)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder))+
        scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 

igm<-igm[!is.na(igm$responder),]
colnames(igm)[15:36]<-paste("IgM",colnames(igm)[15:36], sep="_")
for (i in colnames(igm[15:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igm, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (AU)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder))+
        scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 

```


<!-- # Citos not normalized differenceshigh vs low responders -->


<!-- Timepoints and data: -->

<!-- -D-1: 36 (11 no parasitemia, 25 parasitemia) -->
<!-- -D01: 36 -->
<!-- -D07: 36 -->
<!-- -D21/M0: 36  -->
<!-- -D22/M1: 36  -->
<!-- -D23/M2: 36  -->
<!-- -D35: 36  -->
<!-- -D90: 0 -->

<!-- #P-values adjusted by FDR (all analytes at each timepoint).  -->
<!--  \*:p.adj < 0.05 -->
<!--  \*\*: p.adj < 0.01 -->
<!--  \*\*\*: p.adj < 0.001,  -->
<!--  \*\*\*\*: p.adj < 0.0001.  -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->

<!-- ck<- ck[c(colnames(ck[1:17]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")] -->
<!-- ck[18:50]<-sapply(ck[18:50], log10) -->

<!-- ck$Day<-ifelse(ck$Day=="D21"|ck$Day=="M0", "D21/M0", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D22"|ck$Day=="M1", "D22/M1", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D23"|ck$Day=="M2", "D23/M2", ck$Day) -->
<!-- ck<-ck[!(ck$responder==""),] -->

<!-- ck2<-ck %>% -->
<!--   pivot_longer( -->
<!--     cols = EGF:CXCL13, -->
<!--     names_to = 'analyte', -->
<!--     values_to = 'log10_mfi') -->
<!-- ck2$analyte<- factor(ck2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")) -->

<!-- ck2<-ck2[!ck2$analyte=="IL-17",] -->
<!-- ck2<-ck2%>%filter(!analyte=="IFN-γ" & Day=="D35") -->

<!-- cyto_names<-unique(ck2$analyte) -->
<!-- dfsignificance<-c() -->
<!-- for (j in unique(ck2$Day)){ -->
<!--   ck3<-ck2[ck2$Day==j,] -->
<!--   sigcytoc1<-c() -->
<!--   pvalue<-c() -->
<!--   pvals<-c() -->
<!--   for(i in cyto_names){ -->
<!--       cknew3<-ck3[ck3$analyte==i,] -->
<!--       comparison<-cknew3$responder -->
<!--       pshap<-shapiro.test(cknew3$log10_mfi)$p.value -->
<!--       if (pshap <0.05){ -->
<!--           wilc<-wilcox.test(cknew3$log10_mfi ~ comparison)$p.value -->
<!--           pvals<-c(pvals, wilc) -->
<!--       } -->
<!--       else{ -->
<!--           variance<-var.test(cknew3$log10_mfi ~ comparison)$p.value  -->
<!--           if (variance< 0.05){ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value -->
<!--               pvals<-c(pvals, ttest)      -->
<!--           } -->
<!--           else{ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value -->
<!--               pvals<-c(pvals, ttest)      -->
<!--           } -->
<!--       }} -->
<!--   padj<-p.adjust(pvals,method = "fdr") -->
<!-- dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj)) -->
<!-- } -->
<!-- dfsignificance<-arrange(dfsignificance,Day,analyte) -->

<!-- stat.test2 <- ck2%>% -->
<!--   group_by(analyte, Day) %>% -->
<!--   t_test(log10_mfi ~ responder) %>% -->
<!--   adjust_pvalue()   -->
<!-- stat.test2<-arrange(stat.test2,Day,analyte) -->
<!-- stat.test2$p.adj<-dfsignificance$padj -->
<!-- stat.test2<-stat.test2%>% -->
<!--   add_significance("p.adj")  -->

<!-- stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y")) -->

<!-- for (i in colnames(ck[18:50])[-24]){ -->
<!--   var_name_ticked<-paste0("`", i, "`") -->
<!--   grafic<-ggplot(ck, aes_string("Day", var_name_ticked)) + -->
<!--         #facet_wrap(~ analyte) + -->
<!--         xlab("Day")+ -->
<!--         ylab(bquote("log" [10] (mfi)))+ -->
<!--         geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+ -->
<!--         geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder), shape = ifelse(ck$Volunteer == "BA01009", 18, 4), size=3)+ -->
<!--         scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+ -->
<!--         theme_bw() + -->
<!--         theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), -->
<!--               legend.position = "bottom", legend.direction = "horizontal") + -->
<!--         ggtitle(i)  -->
<!--   print(grafic) -->
<!-- }  -->

<!-- ``` -->

# Citos normalized differences high vs low responders


Timepoints and data:

-D-1: 36 (11 no parasitemia, 25 parasitemia)
-D01: 36
-D07: 36
-D21/M0: 36 
-D22/M1: 36 
-D23/M2: 36 
-D35: 36 
-D90: 0

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 
```{r, message=FALSE, warning=FALSE, echo=FALSE}
cknorm<-cknorm[!is.na(cknorm$responder),]
cknorm<-cknorm[,-44]
cknorm<- cknorm[c(colnames(cknorm[1:16]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")]
cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
cknorm[17:48]<-sapply(cknorm[17:48], log10)
cknorm2<-cknorm %>%
  pivot_longer(
    cols = EGF:CXCL13,
    names_to = 'analyte',
    values_to = 'log10_mfi')

cknorm2$analyte<- factor(cknorm2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13"))


cknorm2<-cknorm2[!cknorm2$Day=="D90",]

cyto_names<-unique(cknorm2$analyte)
dfsignificance<-c()
for (j in unique(cknorm2$Day)){
  cknorm3<-cknorm2[cknorm2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  pvals<-c()
  for(i in cyto_names){
      cknormnew3<-cknorm3[cknorm3$analyte==i,]
      comparison<-cknormnew3$responder
      pshap<-shapiro.test(cknormnew3$log10_mfi)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(cknormnew3$log10_mfi ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(cknormnew3$log10_mfi ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,analyte)

stat.test2 <- cknorm2%>%
  group_by(analyte, Day) %>%
  t_test(log10_mfi ~ responder) %>%
  adjust_pvalue()  
stat.test2<-arrange(stat.test2,Day,analyte)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in colnames(cknorm[17:48])){
  var_name_ticked<-paste0("`", i, "`")
  cknorm<-cknorm[!cknorm$Day=="D90",]
  grafic<-ggplot(cknorm, aes_string("Day", var_name_ticked)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (mfi)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6, outlier.shape=NA, aes(color = responder))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder))+
        scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
 print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(cknorm2$log10_mfi[cknorm2$analyte==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))} 

```


# IgG1 & IgG3 differences high vs low responders


Timepoints and data (depending on antigen, maximum 15):

-D-1: 15 (9 high, 6 low)
-D01: 15
-D07: 15
-D21/M0: 15 
-D22/M1: 15 
-D23/M2: 15 
-D35: 15
-D90: 15

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001.

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg$responder<-factor(igg$responder, levels = c("low", "high"))
igg1<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG1_BACHMI_v02_CarlaS_2023-11-30.csv", sep=";")
igg3<-read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG3_BACHMI_v02_CarlaS_2023-11-30.csv", sep=",")
igg13<-rbind(igg1, igg3)
igg13<-igg13[-15]
igg13<-merge(x = igg13, y = unique(igg[ , c("Volunteer", "responder")]), by = "Volunteer")
igg13.2<-igg13 %>%
  pivot_longer(
    cols = "MSP3":"EXP1",
    names_to = 'antigen',
    values_to = 'log10_mfi')
igg13.2<-igg13.2[igg13.2$log10_mfi<26486.5229,]
igg13.2$log10_mfi<- log10(igg13.2$log10_mfi)
igg13.2$fullname<-paste(igg13.2$Ig, igg13.2$antigen, sep="-")
igg13.2<-igg13.2[!is.na(igg13.2$responder),]
igg13.2$responder<-factor(igg13.2$responder, levels = c("low", "high"))
igg13.2$Day<-ifelse(igg13.2$Day=="D1", "D01", igg13.2$Day)
igg13.2$Day<-ifelse(igg13.2$Day=="D7", "D07", igg13.2$Day)
igg13.2<-igg13.2[!is.na(igg13.2$log10_mfi),]
igg13.2<-igg13.2[!igg13.2$log10_mfi=="-Inf",]

igg13.2$Day<-factor(igg13.2$Day, levels=c("D-1", "D01", "D07", "M0", "M1", "M2", "D35", "D90"))
# igg13.2<-igg13.2[!igg13.2$antigen=="PfRH5",]
# igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-LSA1"& igg13.2$Day=="D01"),]  #Tots els low tenen NAja que els valos abans de log10 eren negatius
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-MSP1_42_3D7" & igg13.2$Day=="D01"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-AMA1_FVO" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-DBLa" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="D35"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH5"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="D01"),]
igg13.2<-igg13.2[!igg13.2$fullname=="IgG3-PfRH4" ,]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="M1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="M2"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-MSP1_42_3D7" & igg13.2$Day=="D35"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="M1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="D35"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-AMA1_3D7" & igg13.2$Day=="D90"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-CelTOS" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="M0"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG1-PfRH4" & igg13.2$Day=="D90"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PfRH5" & igg13.2$Day=="D-1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PfRH5" & igg13.2$Day=="D07"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PfRH5" & igg13.2$Day=="M0"),]

igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-PTRAMP" & igg13.2$Day=="M1"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-EBA175" & igg13.2$Day=="D90"),]
igg13.2<-igg13.2[!(igg13.2$fullname=="IgG3-LSA1" & igg13.2$Day=="D01"),]


# igg[16:36]<-sapply(igg[16:36], log10)

```

## 1. Boxplots of the significant different IgG1 & IgG3 (pval<0.05)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dfsignificance<-c()
for (j in unique(igg13.2$Day)){
  igg13.3<-igg13.2[igg13.2$Day==j,]
  pvals<-c()
  for(i in unique(igg13.3$fullname)){
      ignew3<-igg13.3[igg13.3$fullname==i,]
      comparison<-ignew3$responder
      pshap<-shapiro.test(ignew3$log10_mfi)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(ignew3$log10_mfi ~ comparison)$p.value
          pvals<-c(pvals, wilc)
      }
      else{
          variance<-var.test(ignew3$log10_mfi ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(ignew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(ignew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value
              pvals<-c(pvals, ttest)     
          }
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=unique(igg13.3$fullname), padj=pvals))
}
dfsignificance<-arrange(dfsignificance,Day,fullname)

stat.test2 <- igg13.2%>%
  group_by(fullname, Day) %>%
  wilcox_test(log10_mfi ~ responder) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in unique(dfsignificance$fullname)){
    subset_data<-subset(igg13.2, fullname==i)
    grafic<-ggplot(subset_data, aes(x=Day, y=log10_mfi)) +
        #facet_wrap(~ analyte) +
        xlab("Day")+
        ylab(bquote("log" [10] (mfi)))+
        geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.shape=NA, aes(color = responder))+
        geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder)) +
        scale_colour_manual(values=c("#B2DF8A", "darkgreen"))+
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") +
        ggtitle(i) 
    print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(igg13.2$log10_mfi[igg13.2$fullname==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```
