---
title: "BACHMI_descriptiva"
output:
  html_document:
    df_print: paged
date: "2023-06-30"
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(knitr)
library(dplyr)
gem.cli.df <- readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/NEW_BACHMI_database_20150721_GMP_M0.xlsx")
gem.cli.df[164,16] <- 37.7
gem.cli.df[164,17] <- 1
gem.cli.df[165,16] <- NA
gem.cli.df[165,17] <- NA
gem.cli.df[244,31] <- 0
gem.cli.df <- gem.cli.df[,-c(21:22)]

#Readall database and convert variables into factors

ck <- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/All CK_BACHMI01_22June_Susana_concentracions.csv", sep=";")
ck<-ck [ , c(1:14,45,47,49,15:44,46,48,50)]

colnames(ck)[21:50]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","CXCL13","IL-21","TGF-β")

cknorm<- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/ck_bachmi_susana_normalitzat_.csv", sep=";")

colnames(cknorm)[20:49]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","TGF-β","CXCL13","IL-21")

dc<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/BACHMI DC ALL 22June2015_Susana_frequencies.xlsx")

igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")

#TAULA DESCRIPTIVA
gem.cli.df.un<-gem.cli.df %>% distinct(Volunteer, .keep_all=TRUE)
gem.cli.df.un <- gem.cli.df.un[,-which(colMeans(is.na(gem.cli.df.un)) == 1)]
kable(gem.cli.df.un[,-4])

table(gem.cli.df.un$Route, gem.cli.df.un$sex)
table(gem.cli.df.un$responder_code, gem.cli.df.un$sex)
table(gem.cli.df.un$responder_code, gem.cli.df.un$sex)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
table(gem.cli.df.un$responder_code, gem.cli.df.un$sex)
gem.cli.df.un%>%group_by(responder)
```

# PCA DC

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dcpca<-dc[13:24]
dcpca<-cbind(dc$Label,dcpca)
dcpca<-dcpca[-261,]
dcpca<-dcpca[-87,]
dcpca<-dcpca[-c(6,10)] #Son els CD86+ mDC i CD86+ pDC que tenen 7 i 6 NA. 
M <- log2(dcpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(dcpca$`dc$Label` , pcaResults$x[,1:2])
Original_id<-dcpca$`dc$Label`
library(ggplot2)
dcclin<-dc%>%filter(Label%in%dcpca$`dc$Label`)
lab<-dcclin$Volunteer
lab<-dcclin$Group
lab<-dcclin$Phase
lab<-dcclin$Route
lab<-dcclin$Malaria
lab<-dcclin$sex
lab<-dcclin$responder_code
lab<-dcclin$Day

```


Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-dcclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-dcclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-dcclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```

# Differences DC parasitemia/not parasitemia

```{r, message=FALSE, warning=FALSE, echo=FALSE}

dc$Day<-ifelse(dc$Day=="D21"|dc$Day=="M0", "D21/M0", dc$Day)
dc$Day<-ifelse(dc$Day=="D22"|dc$Day=="M1", "D22/M1", dc$Day)
dc$Day<-ifelse(dc$Day=="D23"|dc$Day=="M2", "D23/M2", dc$Day)
for (i in colnames(dc[13:24])){
  var_name_ticked<-paste0("`", i, "`")
  print(ggplot(dc, aes_string("Day", var_name_ticked)) +
    geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```


# PCA IgG

```{r, message=FALSE, warning=FALSE, echo=FALSE}
igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
iggpca<-igg[16:36]
iggpca<-cbind(igg$Label,iggpca)
M <- log2(iggpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(iggpca$`igg$Label`, pcaResults$x[,1:2])
library(ggplot2)
iggclin<-igg%>%filter(Label%in%iggpca$`igg$Label`)
lab<-iggclin$Volunteer
lab<-iggclin$Group
lab<-iggclin$Phase
lab<-iggclin$Route
lab<-iggclin$Malaria
lab<-iggclin$sex
lab<-iggclin$responder_code
lab<-iggclin$Day


```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-iggclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-iggclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-iggclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```

# Differences IgG parasitemia/not parasitemia


```{r, message=FALSE, warning=FALSE, echo=FALSE}

igg$Day<-ifelse(igg$Day=="D21"|igg$Day=="M0", "D21/M0", igg$Day)
igg$Day<-ifelse(igg$Day=="D22"|igg$Day=="M1", "D22/M1", igg$Day)
igg$Day<-ifelse(igg$Day=="D23"|igg$Day=="M2", "D23/M2", igg$Day)
igg[16:36]<-sapply(igg[16:36], log10)
for (i in colnames(igg[16:36])){
  var_name_ticked<-paste0("`", i, "`")
  print(ggplot(igg, aes_string("Day", var_name_ticked)) +
    geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```

# PCA IgM

```{r, message=FALSE, warning=FALSE, echo=FALSE}
igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")
igmpca<-igm[15:36]
igmpca<-cbind(igm$Label,igmpca)
M <- log2(igmpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(igmpca$`igm$Label`, pcaResults$x[,1:2])
library(ggplot2)
igmclin<-igm%>%filter(Label%in%igmpca$`igm$Label`)
lab<-igmclin$Volunteer
lab<-igmclin$Group
lab<-igmclin$Phase
lab<-igmclin$Route
lab<-igmclin$Malaria
lab<-igmclin$sex
lab<-igmclin$responder_code
lab<-igmclin$Day

```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-igmclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-igmclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-igmclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```


# Differences IgM parasitemia/not parasitemia


```{r, message=FALSE, warning=FALSE, echo=FALSE}

igm$Day<-ifelse(igm$Day=="D21"|igm$Day=="M0", "D21/M0", igm$Day)
igm$Day<-ifelse(igm$Day=="D22"|igm$Day=="M1", "D22/M1", igm$Day)
igm$Day<-ifelse(igm$Day=="D23"|igm$Day=="M2", "D23/M2", igm$Day)
igm[15:36]<-sapply(igm[15:36], log10)
for (i in colnames(igm[15:36])){
  var_name_ticked<-paste0("`", i, "`")
  print(ggplot(igm, aes_string("Day", var_name_ticked)) +
    geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```


# PCA Citos nonorm

```{r, message=FALSE, warning=FALSE, echo=FALSE}
ckpca1<-ck[!ck$Day=="D90",]
ckpca<-ckpca1[18:50]
ckpca<-cbind(ckpca1$Label,ckpca)
M <- log2(ckpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(ckpca$`ckpca1$Label`, pcaResults$x[,1:2])
library(ggplot2)
lab<-ckpca1$Volunteer
lab<-ckpca1$Group
lab<-ckpca1$Phase
lab<-ckpca1$Route
lab<-ckpca1$Malaria
lab<-ckpca1$sex
lab<-ckpca1$responder_code
lab<-ckpca1$Day

```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-ckpca1$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-ckpca1$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-ckpca1$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```

# Citos not normalized differences parasitemia/not parasitemia

```{r, message=FALSE, warning=FALSE, echo=FALSE}

ck$Day<-ifelse(ck$Day=="D21"|ck$Day=="M0", "D21/M0", ck$Day)
ck$Day<-ifelse(ck$Day=="D22"|ck$Day=="M1", "D22/M1", ck$Day)
ck$Day<-ifelse(ck$Day=="D23"|ck$Day=="M2", "D23/M2", ck$Day)
ck[18:50]<-sapply(ck[18:50], log10)
for (i in colnames(ck[18:50])){
  var_name_ticked<-paste0("`", i, "`")
  print(ggplot(ck, aes_string("Day", var_name_ticked)) +
    geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```


# PCA Citos norm

```{r, message=FALSE, warning=FALSE, echo=FALSE}

cknormpca1<-cknorm[!cknorm$Day=="D90",]
cknormpca<-cknormpca1[17:49]
cknormpca<-cbind(cknormpca1$Label,cknormpca)
M <- log2(cknormpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(cknormpca$`cknormpca1$Label`, pcaResults$x[,1:2])
library(ggplot2)
lab<-cknormpca1$Volunteer
lab<-cknormpca1$Group
lab<-cknormpca1$Phase
lab<-cknormpca1$Route
lab<-cknormpca1$Malaria
lab<-cknormpca1$sex
lab<-cknormpca1$responder_code
lab<-cknormpca1$Day

```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-cknormpca1$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-cknormpca1$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-cknormpca1$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)
```


# Citos normalized differences parasitemia/not parasitemia

```{r, message=FALSE, warning=FALSE, echo=FALSE}

cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
cknorm[17:49]<-sapply(cknorm[17:49], log10)
for (i in colnames(cknorm[17:49])){
  var_name_ticknormed<-paste0("`", i, "`")
  print(ggplot(cknorm, aes_string("Day", var_name_ticknormed)) +
    geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```
