---
title: "BACHMI_descriptiva"
output:
  html_document:
    toc: true
    theme: united
    toc_float: true

date: "2023-06-30"
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
library(knitr)
library(dplyr)
library(tidyr)
library(ggpubr)
library(ggbeeswarm)
library(rstatix)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
library(pheatmap)
gem.cli.df <- readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/NEW_BACHMI_database_20150721_GMP_M0.xlsx")
gem.cli.df[164,16] <- 37.7
gem.cli.df[164,17] <- 1
gem.cli.df[165,16] <- NA
gem.cli.df[165,17] <- NA
gem.cli.df[244,31] <- 0
gem.cli.df$Malaria<-factor(gem.cli.df$Malaria, levels = c("parasitemia", "no parasitemia"))

#gem.cli.df <- gem.cli.df[,-c(21:22)]

#Readall database and convert variables into factors

ck <- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/All CK_BACHMI01_22June_Susana_concentracions.csv", sep=";")
ck<-ck [ , c(1:14,45,47,49,15:44,46,48,50)]
ck$Malaria<-factor(ck$Malaria, levels = c("parasitemia", "no parasitemia"))
ck$Day[37]<-"D22"
colnames(ck)[21:50]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","CXCL13","IL-21","TGF-β")

cknorm<- read.csv("C:/Users/csanchez1/Desktop/BACHMI/Datasets/ck_bachmi_susana_normalitzat_.csv", sep=";")
colnames(cknorm)[20:49]<-c("G-CSF","GM-CSF","HGF","IFN-α","IFN-γ","IL-10","IL-12","IL-13","IL-15","IL-1RA","IL-2","IL-2R","IL-4","IL-5","IL-6","IL-8","IP-10","MCP-1","MIG","MIP-1α","MIP-1β","RANTES","TNF-α","VEGF","IL-17","IL-1β","IL-7","TGF-β","CXCL13","IL-21")
cknorm$Malaria<-factor(cknorm$Malaria, levels = c("parasitemia", "no parasitemia"))

dc<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/BACHMI DC ALL 22June2015_Susana_frequencies.xlsx")
dc$Malaria<-factor(dc$Malaria, levels = c("parasitemia", "no parasitemia"))

igm<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgM_BACHMI01_28aug15_Susana.xlsx")
igm$Malaria<-factor(igm$Malaria, levels = c("parasitemia", "no parasitemia"))

igg<-readxl::read_xlsx("C:/Users/csanchez1/Desktop/BACHMI/Datasets/IgG_BACHMI01_7sept15_Guerau.xlsx")
igg$Malaria<-factor(igg$Malaria, levels = c("parasitemia", "no parasitemia"))

#TAULA DESCRIPTIVA
gem.cli.df.un<-gem.cli.df %>% distinct(Volunteer, .keep_all=TRUE)
gem.cli.df.un <- gem.cli.df.un[,-which(colMeans(is.na(gem.cli.df.un)) == 1)]
kable(gem.cli.df.un[,-4])

table(gem.cli.df.un$Route, gem.cli.df.un$sex)
table(gem.cli.df.un$responder_code, gem.cli.df.un$sex)
colnames(gem.cli.df)[15]<-as.character("Time_to_qPCRpos")
colnames(gem.cli.df)[14]<-"Pre_patent_period"
gem.cli.df$Group<-as.factor(gem.cli.df$Group)
```

## Correlation between Time to qPCR+ and Pre patent period.

Dels 25 participants que teneN parasitemia només hi ha aquesta info de 22 (falten BA01018, BA01021, BA01052). Sex: 15 females i 7 males. Responders: 14 high, 8 low.



```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.asp = 0.6, fig.width = 12}
gem.cli.df2<-gem.cli.df
grid.arrange(ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos",ylab="Time to qPCR+", xlab="Pre patent period",
 palette = "jco",  add = "reg.line", conf.int = TRUE) + stat_cor()
, ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos", ylab="Time to qPCR+", xlab="Pre patent period",
   color = "responder", palette = "jco",
   add = "reg.line", conf.int = TRUE) + stat_cor(aes(color = responder))
,ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos",ylab="Time to qPCR+", xlab="Pre patent period",
   color = "Group", palette = "jco",
   add = "reg.line") + stat_cor(aes(color = Group))
,ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos", ylab="Time to qPCR+", xlab="Pre patent period",
   color = "Route", palette = "jco",
   add = "reg.line")+ stat_cor(aes(color = Route))

,ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos", ylab="Time to qPCR+", xlab="Pre patent period",
   color = "Phase", palette = "jco",
   add = "reg.line") + stat_cor(aes(color = Phase))
,ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "Time_to_qPCRpos",ylab="Time to qPCR+", xlab="Pre patent period",
   color = "sex", palette = "jco",
   add = "reg.line") + stat_cor(aes(color = sex)), nrow=2, ncol=3)

```


## Correlation between TBS density and Pre patent period.


```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.asp = 0.6, fig.width = 12}

ggscatter(gem.cli.df2, x = "Pre_patent_period", y = "TBS density", ylab="TBS density", xlab="Pre patent period",
          color = "responder", palette = "jco",
          add = "reg.line", conf.int = TRUE) + stat_cor(aes(color = responder))

```


## Association between TBS density and high or low responder.


```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.asp = 0.6, fig.width = 12}
gem.cli.dfresp<-gem.cli.df[gem.cli.df$Day=="M0",]
gem.cli.dfresp<-gem.cli.dfresp[!is.na(gem.cli.dfresp$responder),]
colnames(gem.cli.dfresp)[13]<-"TBS_density"
ggplot(gem.cli.dfresp, aes(x=responder, y= TBS_density)) +
  geom_boxplot(position=position_dodge(0.8), alpha=0.6,outlier.size=0.3, aes(color = responder))+
  geom_point(position=position_jitterdodge(jitter.width = 0.25), aes(color = responder)) +
  scale_colour_manual(values=c("darkgreen", "#B2DF8A"))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
              legend.position = "bottom", legend.direction = "horizontal") 

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

wilcox.test(gem.cli.dfresp$TBS_density~ gem.cli.dfresp$responder)
```


```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
hemo<- gem.cli.df[,c(20:25)]
hemopca<-cbind(gem.cli.df$Label,hemo)
hemopca<-na.omit(hemopca)
M <- log2(hemopca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(hemopca$`gem.cli.df$Label` , pcaResults$x[,1:2])
Original_id<-hemopca$`gem.cli.df$Label`
hemoclin<-gem.cli.df%>%filter(Label%in%hemopca$`gem.cli.df$Label`)

```

# Hematological data 

## PCA hemo

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-hemoclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-hemoclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-hemoclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)
```


## Differences hemo parasitemia/not parasitemia

Timepoints and data:

-D-1: 24 (2 no parasitemia, 22 parasitemia)
-D01: 0
-D07: 0
-D21/M0: 2 no parasitemia, 22 parasitemia
-D22/M1: 0 no parasitemia, 2 parasitemia
-D23/M2: 0 no parasitemia, 18 parasitemia
-D35: 24 (2 no parasitemia, 22 parasitemia)
-D90: 24

#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}

 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D21"|gem.cli.df$Day=="M0", "D21/M0", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D22"|gem.cli.df$Day=="M1", "D22/M1", gem.cli.df$Day)
 gem.cli.df$Day<-ifelse(gem.cli.df$Day=="D23"|gem.cli.df$Day=="M2", "D23/M2", gem.cli.df$Day)
 hemo2<-gem.cli.df %>%
  pivot_longer(
    cols = Hemoglobin:platelet,
    names_to = 'type',
    values_to = 'counts')
hemo2<-hemo2[!hemo2$Day=="D01"& !hemo2$Day=="D07"& !hemo2$Day=="D22/M1"&!hemo2$Day=="D23/M2",]
dfsignificance<-c()
for (j in unique(hemo2$Day)){
  hemo3<-hemo2[hemo2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  type<-unique(hemo3$type)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in type){
      hemonew3<-hemo3[hemo3$type==i,]
      comparison<-hemonew3$Malaria
      pshap<-shapiro.test(hemonew3$counts)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(hemonew3$counts ~ comparison)$p.value
          pvals<-c(pvals, wilc)
          #wilc<-p.adjust(wilc)
          if (wilc< 0.05){
              sigcytoc1<-c(i,wilc,sigcytoc1)
          }
      }
      else{
          variance<-var.test(hemonew3$counts ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=FALSE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)
              
          }
          else{
              ttest<-t.test(hemonew3$counts ~ comparison, var.equal=TRUE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)     
          }
          if (ttest< 0.05){
              sigcytoc1<-c(i,ttest,sigcytoc1)
              pvalue<-c(ttest,pvalue)}
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, type=type, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,type)

stat.test2 <- hemo2%>%
  group_by(type, Day) %>%
  t_test(counts ~ Malaria) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,type)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

gem.cli.df<-gem.cli.df[!gem.cli.df$Day=="D01"& !gem.cli.df$Day=="D07",]
pd = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.3)

for (i in colnames(gem.cli.df[20:25])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(gem.cli.df, aes_string("Day", var_name_ticked)) +
          geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA, alpha=0.6) +   geom_point(aes(color = Malaria),position = pd)+  ylab(paste(i, "Counts"))
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$type==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(hemo2$counts[hemo2$type==i])))+3) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
 } 

```

# Subpopulations dc

## PCA DC

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dcpca<-dc[13:24]
dcpca<-cbind(dc$Label,dcpca)
dcpca<-dcpca[-261,]
dcpca<-dcpca[-87,]
dcpca<-dcpca[-c(6,10)] #Son els CD86+ mDC i CD86+ pDC que tenen 7 i 6 NA. 
M <- log2(dcpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(dcpca$`dc$Label` , pcaResults$x[,1:2])
Original_id<-dcpca$`dc$Label`
dcclin<-dc%>%filter(Label%in%dcpca$`dc$Label`)
lab<-dcclin$Volunteer
lab<-dcclin$Group
lab<-dcclin$Phase
lab<-dcclin$Route
lab<-dcclin$Malaria
lab<-dcclin$sex
lab<-dcclin$responder_code
lab<-dcclin$Day

```


Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-dcclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-dcclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-dcclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```

## Differences DC parasitemia/not parasitemia

Timepoints and data:

-D-1: 36 (11 no parasitemia, 25 parasitemia)
-D01: 36
-D07: 36
-D21/M0: 36 
-D22/M1: 35 (11 no parasitemia, 24 parasitemia)
-D23/M2: 36 
-D35: 36 
-D90: 36
```{r, message=FALSE, warning=FALSE, echo=FALSE}
# 
 dc$Day<-ifelse(dc$Day=="D21"|dc$Day=="M0", "D21/M0", dc$Day)
 dc$Day<-ifelse(dc$Day=="D22"|dc$Day=="M1", "D22/M1", dc$Day)
 dc$Day<-ifelse(dc$Day=="D23"|dc$Day=="M2", "D23/M2", dc$Day)
# for (i in colnames(dc[13:24])){
#   var_name_ticked<-paste0("`", i, "`")
#   print(ggplot(dc, aes_string("Day", var_name_ticked)) +
#     geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 
```


#P-values adjusted by FDR (all cell_populations at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dc2<-dc %>%
  pivot_longer(
    cols = Lymphos:"immature DC",
    names_to = 'cell_population',
    values_to = 'freq')

dfsignificance<-c()
for (j in unique(dc2$Day)){
  dc3<-dc2[dc2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  cells<-unique(dc3$cell_population)
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in cells){
      dcnew3<-dc3[dc3$cell_population==i,]
      comparison<-dcnew3$Malaria
      pshap<-shapiro.test(dcnew3$freq)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(dcnew3$freq ~ comparison)$p.value
          pvals<-c(pvals, wilc)
          #wilc<-p.adjust(wilc)
          if (wilc< 0.05){
              sigcytoc1<-c(i,wilc,sigcytoc1)
          }
      }
      else{
          variance<-var.test(dcnew3$freq ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=FALSE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)
              
          }
          else{
              ttest<-t.test(dcnew3$freq ~ comparison, var.equal=TRUE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)     
          }
          if (ttest< 0.05){
              sigcytoc1<-c(i,ttest,sigcytoc1)
              pvalue<-c(ttest,pvalue)}
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, cells=cells, padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,cells)

stat.test2 <- dc2%>%
  group_by(cell_population, Day) %>%
  t_test(freq ~ Malaria) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,cell_population)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))

for (i in colnames(dc[13:24])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(dc, aes_string("Day", var_name_ticked)) +
          geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA, alpha=0.6)+     geom_point(aes(color = Malaria),position = pd)+ ylab(paste("Frequency ",i, "(%))"))
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$cell_population==i,], label = "p.adj.signif", hide.ns = TRUE, y.position = max((na.omit(dc2$freq[dc2$cell_population==i])))+3) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
 } 


```

# IgG & IgM

## PCA IgG

```{r, message=FALSE, warning=FALSE, echo=FALSE}
iggpca<-igg[16:36]
iggpca<-cbind(igg$Label,iggpca)
M <- log2(iggpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(iggpca$`igg$Label`, pcaResults$x[,1:2])
iggclin<-igg%>%filter(Label%in%iggpca$`igg$Label`)
lab<-iggclin$Volunteer
lab<-iggclin$Group
lab<-iggclin$Phase
lab<-iggclin$Route
lab<-iggclin$Malaria
lab<-iggclin$sex
lab<-iggclin$responder_code
lab<-iggclin$Day
```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-iggclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-iggclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-iggclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```

## PCA IgM

```{r, message=FALSE, warning=FALSE, echo=FALSE}
igmpca<-igm[15:36]
igmpca<-cbind(igm$Label,igmpca)
M <- log2(igmpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(igmpca$`igm$Label`, pcaResults$x[,1:2])
igmclin<-igm%>%filter(Label%in%igmpca$`igm$Label`)
lab<-igmclin$Volunteer
lab<-igmclin$Group
lab<-igmclin$Phase
lab<-igmclin$Route
lab<-igmclin$Malaria
lab<-igmclin$sex
lab<-igmclin$responder_code
lab<-igmclin$Day

```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-igmclin$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-igmclin$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-igmclin$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)

```


## Differences IgG & IgM parasitemia/not parasitemia


All timepoints 36 participants. 

P-values adjusted by FDR (all antibodies at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}


igm[15:36]<-sapply(igm[15:36], log10)
igm$Day<-ifelse(igm$Day=="D21"|igm$Day=="M0", "D21/M0", igm$Day)
igm$Day<-ifelse(igm$Day=="D22"|igm$Day=="M1", "D22/M1", igm$Day)
igm$Day<-ifelse(igm$Day=="D23"|igm$Day=="M2", "D23/M2", igm$Day)
colnames(igm)[15:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4",
"PfRH5","MSP-1 19","BSA","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2",
"DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igm2<-igm %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')

igm2$fullname<-paste(igm2$Ig, igm2$antigen, sep="_")


igg[16:36]<-sapply(igg[16:36], log10)
igg$Day<-ifelse(igg$Day=="D21"|igg$Day=="M0", "D21/M0", igg$Day)
igg$Day<-ifelse(igg$Day=="D22"|igg$Day=="M1", "D22/M1", igg$Day)
igg$Day<-ifelse(igg$Day=="D23"|igg$Day=="M2", "D23/M2", igg$Day)
colnames(igg)[16:36]<-c("MSP-3","PTRAMP","PfAARP","PfRH1","PfRH2","PfRH4",
"PfRH5","MSP-1 19","AMA-1[3D7]","AMA-1[FVO]","MSP-1 42[3D7]","MSP-1 42[FVO]","EBA-175","CelTOS","LSA-1","SSP-2","DBLa","CSP","CyRPA-1","CyRPA-2","EXP-1")
igg2<-igg %>%
  pivot_longer(
    cols = "MSP-3":"EXP-1",
    names_to = 'antigen',
    values_to = 'log10_conc')
igg2$fullname<-paste(igg2$Ig, igg2$antigen, sep="_")
igg2<-igg2[,-15]
ig2<-rbind(igm2, igg2)
dfsignificance<-c()
for (j in unique(ig2$Day)){
  ig3<-ig2[ig2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  #cyto_names<-cyto_names[-25]
  pvals<-c()
  for(i in unique(ig3$fullname)){
      ignew3<-ig3[ig3$fullname==i,]
      comparison<-ignew3$Malaria
      pshap<-shapiro.test(ignew3$log10_conc)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(ignew3$log10_conc ~ comparison)$p.value
          pvals<-c(pvals, wilc)
          #wilc<-p.adjust(wilc)
          if (wilc< 0.05){
              sigcytoc1<-c(i,wilc,sigcytoc1)
          }
      }
      else{
          variance<-var.test(ignew3$log10_conc ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=FALSE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)
          }
          else{
              ttest<-t.test(ignew3$log10_conc ~ comparison, var.equal=TRUE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)     
          }
          if (ttest< 0.05){
              sigcytoc1<-c(i,ttest,sigcytoc1)
              pvalue<-c(ttest,pvalue)}
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, fullname=unique(ig3$fullname), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,fullname)

stat.test2 <- ig2%>%
  group_by(fullname, Day) %>%
  t_test(log10_conc ~ Malaria) %>%
  adjust_pvalue() 
stat.test2<-arrange(stat.test2,Day,fullname)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))
pd = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.3)

colnames(igg)[16:36]<-paste("IgG",colnames(igg)[16:36], sep="_")
for (i in colnames(igg[16:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igg, aes_string("Day", var_name_ticked)) +
          geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA, alpha=0.6)+     geom_point(aes(color = Malaria),position = pd)+ylab(paste("log10(",i, ")"))
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 

colnames(igm)[15:36]<-paste("IgM",colnames(igm)[15:36], sep="_")
for (i in colnames(igm[15:36])){
  var_name_ticked<-paste0("`", i, "`")
  grafic<-ggplot(igm, aes_string("Day", var_name_ticked)) +
          geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA, alpha=0.6)+geom_point(aes(color = Malaria),position = pd)+ ylab(paste("log10(",i, ")"))
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$fullname==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ig2$log10_conc[ig2$fullname==i])))+1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```


# Heatmap IgG parasitemia/not parasitemia


```{r, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=15, fig.width=12}
igp<-as.matrix(igg[16:36])

annotation_row<-data.frame(igg$Volunteer, igg$sex, igg$Day)
colnames(annotation_row)<-c("Volunteeer", "Sex", "Day")

rownames(annotation_row)<-igg$Label
rownames(igp)<-rownames(annotation_row)
annotation_colors = list(Sex = c("Male"="#F8766D", "Female"="#00BFC4"), Volunteer=c( colorRampPalette(brewer.pal(8, "Set2"))(36)), colorRampPalette(brewer.pal(8, "Set1"))(8))
 names(annotation_colors[[2]])<-unique(igg$Volunteer)
 names(annotation_colors[[3]])<-c("D-1","D01","D07", "M0","M1","M2", "D35","D90")

pheatmap(igp,  show_rownames = FALSE, fontsize = 16, annotation_row=annotation_row, annotation_colors = annotation_colors, annotation_names_col = FALSE)
```
# Heatmap IgM parasitemia/not parasitemia


\renewcommand{\arraystretch}{0.85}
```{r, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=15, fig.width=12}
igm<-igm[-23]

imp<-as.matrix(igm[15:35])

annotation_row<-data.frame(igm$Volunteer,igm$sex, igm$Day)
colnames(annotation_row)<-c("Volunteeer","Sex","Day")

rownames(annotation_row)<-igm$Label
rownames(imp)<-rownames(annotation_row)

annotation_colors = list(Sex = c("Male"="#F8766D", "Female"="#00BFC4"), Volunteer=c( colorRampPalette(brewer.pal(8, "Set2"))(36)), colorRampPalette(brewer.pal(8, "Set1"))(8))
 names(annotation_colors[[2]])<-unique(igm$Volunteer)
 names(annotation_colors[[3]])<-c(unique(igm$Day))
pheatmap(imp, show_rownames = FALSE, fontsize = 16, annotation_row=annotation_row, annotation_colors = annotation_colors, annotation_names_col = FALSE)
```

<!-- # PCA Citos nonorm -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- ckpca1<-ck[!ck$Day=="D90",] -->
<!-- ckpca<-ckpca1[18:50] -->
<!-- ckpca<-cbind(ckpca1$Label,ckpca) -->
<!-- M <- log2(ckpca[-1] + 1) -->
<!-- pcaResults <- prcomp(M) -->
<!-- pcplot<-data.frame(ckpca$`ckpca1$Label`, pcaResults$x[,1:2]) -->
<!-- lab<-ckpca1$Volunteer -->
<!-- lab<-ckpca1$Group -->
<!-- lab<-ckpca1$Phase -->
<!-- lab<-ckpca1$Route -->
<!-- lab<-ckpca1$Malaria -->
<!-- lab<-ckpca1$sex -->
<!-- lab<-ckpca1$responder_code -->
<!-- lab<-ckpca1$Day -->

<!-- ck$Day<-ifelse(ck$Day=="D21"|ck$Day=="M0", "D21/M0", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D22"|ck$Day=="M1", "D22/M1", ck$Day) -->
<!-- ck$Day<-ifelse(ck$Day=="D23"|ck$Day=="M2", "D23/M2", ck$Day) -->
<!-- ``` -->

<!-- Volunteer -->


<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->

<!-- lab<-ckpca1$Volunteer -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none") -->
<!-- lab<-ckpca1$Day -->

<!-- Day<-as.factor(lab) -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Day) -->

<!-- Malaria<-ckpca1$Malaria -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria) -->

<!-- ``` -->
<!-- # PCA Citos nonorm Plate (Luminex, CXCL13, IL21 i TGFB) -->


<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->

<!-- Plate.Luminex<-as.factor(ckpca1$Plate.Luminex) -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.Luminex) -->


<!-- Plate.CXCL13<-as.factor(ckpca1$plate_CXCL13) -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.CXCL13) -->


<!-- Plate.IL21<-as.factor(ckpca1$plate_IL21) -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.IL21) -->


<!-- Plate.TGFb<-as.factor(ckpca1$plate_TGFb) -->
<!-- qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.TGFb) -->

<!-- ``` -->

<!-- # Citos not normalized differences parasitemia/not parasitemia -->


<!-- Timepoints and data: -->

<!-- -D-1: 36 (11 no parasitemia, 25 parasitemia) -->
<!-- -D01: 36 -->
<!-- -D07: 36 -->
<!-- -D21/M0: 36  -->
<!-- -D22/M1: 36  -->
<!-- -D23/M2: 36  -->
<!-- -D35: 36  -->
<!-- -D90: 0 -->

<!-- #P-values adjusted by FDR (all analytes at each timepoint).  -->
<!--  \*:p.adj < 0.05 -->
<!--  \*\*: p.adj < 0.01 -->
<!--  \*\*\*: p.adj < 0.001,  -->
<!--  \*\*\*\*: p.adj < 0.0001.  -->

<!-- ```{r, message=FALSE, warning=FALSE, echo=FALSE} -->
<!-- #  -->
<!-- # ck$Day<-ifelse(ck$Day=="D21"|ck$Day=="M0", "D21/M0", ck$Day) -->
<!-- # ck$Day<-ifelse(ck$Day=="D22"|ck$Day=="M1", "D22/M1", ck$Day) -->
<!-- # ck$Day<-ifelse(ck$Day=="D23"|ck$Day=="M2", "D23/M2", ck$Day) -->
<!-- # ck[18:50]<-sapply(ck[18:50], log10) -->
<!-- # for (i in colnames(ck[18:50])){ -->
<!-- #   var_name_ticked<-paste0("`", i, "`") -->
<!-- #   print(ggplot(ck, aes_string("Day", var_name_ticked)) + -->
<!-- #     geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) }  -->


<!-- ck<- ck[c(colnames(ck[1:17]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")] -->
<!-- ck[18:50]<-sapply(ck[18:50], log10) -->
<!-- ck2<-ck %>% -->
<!--   pivot_longer( -->
<!--     cols = EGF:CXCL13, -->
<!--     names_to = 'analyte', -->
<!--     values_to = 'log10_mfi') -->
<!-- ck2$analyte<- factor(ck2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")) -->

<!-- ck2<-ck2[!ck2$Day=="D90",] -->
<!-- ck2<-ck2[!ck2$analyte=="IL-17",] -->

<!-- cyto_names<-unique(ck2$analyte) -->
<!-- dfsignificance<-c() -->
<!-- for (j in unique(ck2$Day)){ -->
<!--   ck3<-ck2[ck2$Day==j,] -->
<!--   sigcytoc1<-c() -->
<!--   pvalue<-c() -->
<!--   pvals<-c() -->
<!--   for(i in cyto_names){ -->
<!--       cknew3<-ck3[ck3$analyte==i,] -->
<!--       comparison<-cknew3$Malaria -->
<!--       pshap<-shapiro.test(cknew3$log10_mfi)$p.value -->
<!--       if (pshap <0.05){ -->
<!--           wilc<-wilcox.test(cknew3$log10_mfi ~ comparison)$p.value -->
<!--           pvals<-c(pvals, wilc) -->
<!--           #wilc<-p.adjust(wilc) -->
<!--           if (wilc< 0.05){ -->
<!--               sigcytoc1<-c(i,wilc,sigcytoc1) -->
<!--           } -->
<!--       } -->
<!--       else{ -->
<!--           variance<-var.test(cknew3$log10_mfi ~ comparison)$p.value  -->
<!--           if (variance< 0.05){ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value -->
<!--               #ttest<-p.adjust(ttest) -->
<!--               pvals<-c(pvals, ttest) -->

<!--           } -->
<!--           else{ -->
<!--               ttest<-t.test(cknew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value -->
<!--               #ttest<-p.adjust(ttest) -->
<!--               pvals<-c(pvals, ttest)      -->
<!--           } -->
<!--           if (ttest< 0.05){ -->
<!--               sigcytoc1<-c(i,ttest,sigcytoc1) -->
<!--               pvalue<-c(ttest,pvalue)} -->
<!--       }} -->
<!--   padj<-p.adjust(pvals,method = "fdr") -->
<!-- dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj)) -->
<!-- } -->
<!-- dfsignificance<-arrange(dfsignificance,Day,analyte) -->

<!-- stat.test2 <- ck2%>% -->
<!--   group_by(analyte, Day) %>% -->
<!--   t_test(log10_mfi ~ Malaria) %>% -->
<!--   adjust_pvalue()   -->
<!-- stat.test2<-arrange(stat.test2,Day,analyte) -->
<!-- stat.test2$p.adj<-dfsignificance$padj -->
<!-- stat.test2<-stat.test2%>% -->
<!--   add_significance("p.adj")  -->

<!-- stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y")) -->


<!-- for (i in colnames(ck[18:50])[-24]){ -->
<!--   var_name_ticked<-paste0("`", i, "`") -->
<!--   grafic<-ggplot(ck, aes_string("Day", var_name_ticked)) + -->
<!--           geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA) +     geom_point(aes(color = Malaria),position = pd) -->
<!--   print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(ck2$log10_mfi[ck2$analyte==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))) -->
<!-- }  -->
<!-- ``` -->

# Cytokines

## PCA Citos norm

```{r, message=FALSE, warning=FALSE, echo=FALSE}

cknormpca1<-cknorm[!cknorm$Day=="D90",]
cknormpca<-cknormpca1[17:49]
cknormpca<-cbind(cknormpca1$Label,cknormpca)
M <- log2(cknormpca[-1] + 1)
pcaResults <- prcomp(M)
pcplot<-data.frame(cknormpca$`cknormpca1$Label`, pcaResults$x[,1:2])
lab<-cknormpca1$Volunteer
lab<-cknormpca1$Group
lab<-cknormpca1$Phase
lab<-cknormpca1$Route
lab<-cknormpca1$Malaria
lab<-cknormpca1$sex
lab<-cknormpca1$responder_code
lab<-cknormpca1$Day

```

Volunteer


```{r, message=FALSE, warning=FALSE, echo=FALSE}

lab<-cknormpca1$Volunteer
qplot(x=PC1, y=PC2, data=pcplot, colour=lab)+ theme(legend.position = "none")
lab<-cknormpca1$Day

Day<-as.factor(lab)
qplot(x=PC1, y=PC2, data=pcplot, colour=Day)

Malaria<-cknormpca1$Malaria
qplot(x=PC1, y=PC2, data=pcplot, colour=Malaria)
```
## PCA Citos norm Plate (Luminex, CXCL13, IL21 i TGFB)


```{r, message=FALSE, warning=FALSE, echo=FALSE}

Plate.Luminex<-as.factor(cknormpca1$plate.Luminex)
qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.Luminex)


Plate.CXCL13<-as.factor(cknormpca1$plate_CXCL13)
qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.CXCL13)


Plate.IL21<-as.factor(cknormpca1$plate_IL21)
qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.IL21)


Plate.TGFb<-as.factor(cknormpca1$plate_TGFb)
qplot(x=PC1, y=PC2, data=pcplot, colour=Plate.TGFb)

```

## Citos normalized differences parasitemia/not parasitemia


Timepoints and data:

-D-1: 36 (11 no parasitemia, 25 parasitemia)
-D01: 36
-D07: 36
-D21/M0: 36 
-D22/M1: 36 
-D23/M2: 36 
-D35: 36 
-D90: 0

#P-values adjusted by FDR (all analytes at each timepoint). 
 \*:p.adj < 0.05
 \*\*: p.adj < 0.01
 \*\*\*: p.adj < 0.001, 
 \*\*\*\*: p.adj < 0.0001. 
```{r, message=FALSE, warning=FALSE, echo=FALSE}
# 
# cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
# cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
# cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
# cknorm[17:49]<-sapply(cknorm[17:49], log10)
# for (i in colnames(cknorm[17:49])){
#   var_name_ticknormed<-paste0("`", i, "`")
#   print(ggplot(cknorm, aes_string("Day", var_name_ticknormed)) +
#     geom_boxplot(position=position_dodge(1), aes(fill=Malaria))) } 

cknorm<- cknorm[c(colnames(cknorm[1:16]),"EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13")]
cknorm$Day<-ifelse(cknorm$Day=="D21"|cknorm$Day=="M0", "D21/M0", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D22"|cknorm$Day=="M1", "D22/M1", cknorm$Day)
cknorm$Day<-ifelse(cknorm$Day=="D23"|cknorm$Day=="M2", "D23/M2", cknorm$Day)
cknorm[17:49]<-sapply(cknorm[17:49], log10)
cknorm2<-cknorm %>%
  pivot_longer(
    cols = EGF:CXCL13,
    names_to = 'analyte',
    values_to = 'log10_mfi')
cknorm2$analyte<- factor(cknorm2$analyte, levels = c("EGF", "FGF", "G-CSF", "GM-CSF","HGF","VEGF","TNF-α","TGF-β","IFN-α", "IFN-γ", "IL-1RA", "IL-1β", "IL-2","IL-2R","IL-4","IL-5","IL-6","IL-7","IL-8","IL-10","IL-12","IL-13","IL-15", "IL-17","IL-21", "IP-10", "MCP-1", "MIG","MIP-1α", "MIP-1β", "EOTAXIN", "RANTES","CXCL13"))

cknorm2<-cknorm2[!cknorm2$Day=="D90",]
cknorm2<-cknorm2[!cknorm2$analyte=="IL-17",]

cyto_names<-unique(cknorm2$analyte)
dfsignificance<-c()
for (j in unique(cknorm2$Day)){
  cknorm3<-cknorm2[cknorm2$Day==j,]
  sigcytoc1<-c()
  pvalue<-c()
  pvals<-c()
  for(i in cyto_names){
      cknormnew3<-cknorm3[cknorm3$analyte==i,]
      comparison<-cknormnew3$Malaria
      pshap<-shapiro.test(cknormnew3$log10_mfi)$p.value
      if (pshap <0.05){
          wilc<-wilcox.test(cknormnew3$log10_mfi ~ comparison)$p.value
          pvals<-c(pvals, wilc)
          #wilc<-p.adjust(wilc)
          if (wilc< 0.05){
              sigcytoc1<-c(i,wilc,sigcytoc1)
          }
      }
      else{
          variance<-var.test(cknormnew3$log10_mfi ~ comparison)$p.value 
          if (variance< 0.05){
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=FALSE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)
              
          }
          else{
              ttest<-t.test(cknormnew3$log10_mfi ~ comparison, var.equal=TRUE)$p.value
              #ttest<-p.adjust(ttest)
              pvals<-c(pvals, ttest)     
          }
          if (ttest< 0.05){
              sigcytoc1<-c(i,ttest,sigcytoc1)
              pvalue<-c(ttest,pvalue)}
      }}
  padj<-p.adjust(pvals,method = "fdr")
dfsignificance<-rbind(dfsignificance,data.frame(Day=j, analyte=unique(cyto_names), padj=padj))
}
dfsignificance<-arrange(dfsignificance,Day,analyte)

stat.test2 <- cknorm2%>%
  group_by(analyte, Day) %>%
  t_test(log10_mfi ~ Malaria) %>%
  adjust_pvalue()  
stat.test2<-arrange(stat.test2,Day,analyte)
stat.test2$p.adj<-dfsignificance$padj
stat.test2<-stat.test2%>%
  add_significance("p.adj") 

stat.test2 <- stat.test2 %>% add_xy_position(x = "Day", scales = c("free_y"))


for (i in colnames(cknorm[17:49])[-24]){
  var_name_ticknormed<-paste0("`", i, "`")
  cknorm<-cknorm[!cknorm$Day=="D90",]
  grafic<-ggplot(cknorm, aes_string("Day", var_name_ticknormed)) +
          geom_boxplot(position=position_dodge(1), aes(fill=Malaria), outlier.shape = NA, alpha=0.6)+     geom_point(aes(color = Malaria),position = pd) + ylab(paste("log10(",i, ")"))
  print(grafic+stat_pvalue_manual(stat.test2[stat.test2$analyte==i,], label = "p.adj.signif", hide.ns = TRUE,  y.position = max((na.omit(cknorm2$log10_mfi[cknorm2$analyte==i])))+0.1) +scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))))
} 
```


